SMASH companion source code repository

### 2018-12-21 analysis/index.Rmd
wflow_publish(c("index.Rmd", "poisson.Rmd"))

+ The `output` directory contains results from the Gaussian and
  Poisson simulations. File `pois_hf.RData` contains results from
  experimenting with different Gaussian denoising techniques for the
  Haar-Fisz algorithm in the Poisson simulations.

>>>>

+ The `output` directory contains results from the Gaussian and
  Poisson simulations. The `pois_hf.RData` file in this directory
  contains results from experimenting with different Gaussian
  denoising techniques for the Haar-Fisz algorithm in the Poisson
  simulations.
